\section{Problem Statement and Opportunity}

\subsection{The Practical Problem}

Modern teams exchange structured data through APIs, spreadsheets, configuration files, dashboards, ETL jobs, notebooks, and AI tools. JSON, YAML, and CSV are everywhere, but everyday workflows remain surprisingly fragile:

\begin{itemize}
  \item A user may not know whether a file is valid, what schema it follows, or how to safely convert it.
  \item Developers often need repeatable conversion logic, not a one-off answer from a chatbot.
  \item Non-technical users need explanations of fields, rows, anomalies, and business meaning.
  \item LLM-only systems can produce plausible but invalid JSON, invent fields, or ignore schema constraints.
  \item Real workflows require logs, versioned schemas, approvals, access control, and traceability.
\end{itemize}

The gap is not simply ``format conversion.'' The gap is collaborative structured-data operations: people need a system that can understand an instruction, inspect the data, retrieve the right schema context, perform the transformation exactly, explain the result, and prove what happened.

\subsection{Opportunity for the OJT Project}

\projectname{} is a strong OJT project because it demonstrates several high-value engineering capabilities in a compact product:

\begin{itemize}
  \item \textbf{Backend engineering:} FastAPI endpoints, typed request/response models, storage, and deployment.
  \item \textbf{AI integration:} foundation model gateway, prompt contracts, retrieval, and explanation generation.
  \item \textbf{Agent orchestration:} multi-step workflows, shared state, role-specific agents, and progress events.
  \item \textbf{Protocol design:} MCP tool/resource/prompt servers for modular capabilities.
  \item \textbf{Reliability:} schema validation, deterministic conversion, round-trip checks, tests, and audit logs.
  \item \textbf{Governance:} prompt-injection defenses, sensitive-data checks, human review, and risk documentation.
\end{itemize}

\subsection{Target Users}

\begin{tabularx}{\textwidth}{p{0.22\textwidth}X}
\toprule
\textbf{User group} & \textbf{Value proposition} \\
\midrule
Analysts & Convert and explain files without manually writing scripts for every schema variation. \\
Developers & Validate API payloads, generate transformation reports, and expose repeatable workflows through APIs. \\
Project reviewers & See a complete AI system that combines models, agents, tools, RAG, security, and deployment. \\
Future enterprise teams & Extend the same architecture to databases, drives, workflow systems, and domain-specific schema registries. \\
\bottomrule
\end{tabularx}

