\section{References}

\begin{thebibliography}{99}

\bibitem{bommasani2021foundation}
R. Bommasani et al.
\newblock \textit{On the Opportunities and Risks of Foundation Models}.
\newblock Stanford Center for Research on Foundation Models, 2021.
\newblock \url{https://crfm.stanford.edu/report.html}

\bibitem{lewis2020rag}
P. Lewis et al.
\newblock \textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}.
\newblock Advances in Neural Information Processing Systems 33, 2020.
\newblock \url{https://arxiv.org/abs/2005.11401}

\bibitem{gao2022hyde}
L. Gao, X. Ma, J. Lin, and J. Callan.
\newblock \textit{Precise Zero-Shot Dense Retrieval without Relevance Labels}.
\newblock arXiv:2212.10496, 2022.
\newblock \url{https://arxiv.org/abs/2212.10496}

\bibitem{sarthi2024raptor}
P. Sarthi et al.
\newblock \textit{RAPTOR: Recursive Abstractive Processing for Tree-Organized Retrieval}.
\newblock arXiv:2401.18059, 2024.
\newblock \url{https://arxiv.org/abs/2401.18059}

\bibitem{edge2024graphrag}
D. Edge et al.
\newblock \textit{From Local to Global: A Graph RAG Approach to Query-Focused Summarization}.
\newblock arXiv:2404.16130, 2024.
\newblock \url{https://arxiv.org/abs/2404.16130}

\bibitem{microsoftGraphRagDocs}
Microsoft.
\newblock \textit{GraphRAG Documentation: Indexing Overview and Query Methods}.
\newblock \url{https://microsoft.github.io/graphrag/index/overview/}

\bibitem{khattab2020colbert}
O. Khattab and M. Zaharia.
\newblock \textit{ColBERT: Efficient and Effective Passage Search via Contextualized Late Interaction over BERT}.
\newblock SIGIR, 2020.
\newblock \url{https://people.eecs.berkeley.edu/~matei/papers/2020/sigir_colbert.pdf}

\bibitem{thakur2021beir}
N. Thakur, N. Reimers, A. Rücklé, A. Srivastava, and I. Gurevych.
\newblock \textit{BEIR: A Heterogeneous Benchmark for Zero-shot Evaluation of Information Retrieval Models}.
\newblock arXiv:2104.08663, 2021.
\newblock \url{https://arxiv.org/abs/2104.08663}

\bibitem{guo2024lightrag}
Z. Guo et al.
\newblock \textit{LightRAG: Simple and Fast Retrieval-Augmented Generation}.
\newblock arXiv:2410.05779, 2024.
\newblock \url{https://arxiv.org/abs/2410.05779}

\bibitem{mavromatis2024gnnrag}
C. Mavromatis and G. Karypis.
\newblock \textit{GNN-RAG: Graph Neural Retrieval for Large Language Model Reasoning}.
\newblock arXiv:2405.20139, 2024.
\newblock \url{https://arxiv.org/abs/2405.20139}

\bibitem{fdaTransparency}
U.S. Food and Drug Administration, Health Canada, and Medicines and Healthcare products Regulatory Agency.
\newblock \textit{Transparency for Machine Learning-Enabled Medical Devices: Guiding Principles}.
\newblock 2024.
\newblock \url{https://www.fda.gov/medical-devices/software-medical-device-samd/transparency-machine-learning-enabled-medical-devices-guiding-principles}

\bibitem{vasey2022decide}
B. Vasey et al.
\newblock \textit{Reporting Guideline for the Early-Stage Clinical Evaluation of Decision Support Systems Driven by Artificial Intelligence: DECIDE-AI}.
\newblock Nature Medicine, 2022.
\newblock \url{https://doi.org/10.1038/s41591-022-01772-9}

\bibitem{chen2024medEval}
Y. Chen et al.
\newblock \textit{Evaluating Large Language Models in Medical Applications: A Survey}.
\newblock arXiv:2405.07468, 2024.
\newblock \url{https://arxiv.org/abs/2405.07468}

\bibitem{zhao2024llmExplainability}
H. Zhao et al.
\newblock \textit{From Understanding to Utilization: A Survey on Explainability for Large Language Models}.
\newblock arXiv:2401.12874, 2024.
\newblock \url{https://arxiv.org/abs/2401.12874}

\bibitem{huang2024selfExplanations}
F. Huang et al.
\newblock \textit{Are Self-Explanations from Large Language Models Faithful?}
\newblock Findings of ACL, 2024.
\newblock \url{https://arxiv.org/abs/2401.07927}

\bibitem{jain2019attention}
S. Jain and B. C. Wallace.
\newblock \textit{Attention is not Explanation}.
\newblock NAACL, 2019.
\newblock \url{https://arxiv.org/abs/1902.10186}

\bibitem{ribeiro2016lime}
M. T. Ribeiro, S. Singh, and C. Guestrin.
\newblock \textit{``Why Should I Trust You?'': Explaining the Predictions of Any Classifier}.
\newblock KDD, 2016.
\newblock \url{https://arxiv.org/abs/1602.04938}

\bibitem{lundberg2017shap}
S. M. Lundberg and S.-I. Lee.
\newblock \textit{A Unified Approach to Interpreting Model Predictions}.
\newblock NeurIPS, 2017.
\newblock \url{https://arxiv.org/abs/1705.07874}

\bibitem{sundararajan2017ig}
M. Sundararajan, A. Taly, and Q. Yan.
\newblock \textit{Axiomatic Attribution for Deep Networks}.
\newblock ICML, 2017.
\newblock \url{https://arxiv.org/abs/1703.01365}

\bibitem{kim2018tcav}
B. Kim et al.
\newblock \textit{Interpretability Beyond Feature Attribution: Quantitative Testing with Concept Activation Vectors}.
\newblock ICML, 2018.
\newblock \url{https://arxiv.org/abs/1711.11279}

\bibitem{gao2021simcse}
T. Gao, X. Yao, and D. Chen.
\newblock \textit{SimCSE: Simple Contrastive Learning of Sentence Embeddings}.
\newblock EMNLP, 2021.
\newblock \url{https://arxiv.org/abs/2104.08821}

\bibitem{izacard2021contriever}
G. Izacard et al.
\newblock \textit{Unsupervised Dense Information Retrieval with Contrastive Learning}.
\newblock arXiv:2112.09118, 2021.
\newblock \url{https://arxiv.org/abs/2112.09118}

\bibitem{wang2022e5}
L. Wang et al.
\newblock \textit{Text Embeddings by Weakly-Supervised Contrastive Pre-training}.
\newblock arXiv:2212.03533, 2022.
\newblock \url{https://arxiv.org/abs/2212.03533}

\bibitem{neelakantan2022textcode}
A. Neelakantan et al.
\newblock \textit{Text and Code Embeddings by Contrastive Pre-Training}.
\newblock arXiv:2201.10005, 2022.
\newblock \url{https://arxiv.org/abs/2201.10005}

\bibitem{wang2021tsdae}
K. Wang, N. Reimers, and I. Gurevych.
\newblock \textit{TSDAE: Using Transformer-based Sequential Denoising Auto-Encoder for Unsupervised Sentence Embedding Learning}.
\newblock Findings of EMNLP, 2021.
\newblock \url{https://arxiv.org/abs/2104.06979}

\bibitem{grill2020byol}
J.-B. Grill et al.
\newblock \textit{Bootstrap Your Own Latent: A New Approach to Self-Supervised Learning}.
\newblock NeurIPS, 2020.
\newblock \url{https://arxiv.org/abs/2006.07733}

\bibitem{zbontar2021barlow}
J. Zbontar et al.
\newblock \textit{Barlow Twins: Self-Supervised Learning via Redundancy Reduction}.
\newblock ICML, 2021.
\newblock \url{https://arxiv.org/abs/2103.03230}

\bibitem{bahri2021scarf}
D. Bahri, H. Jiang, Y. Tay, and D. Metzler.
\newblock \textit{SCARF: Self-Supervised Contrastive Learning using Random Feature Corruption}.
\newblock arXiv:2106.15147, 2021.
\newblock \url{https://arxiv.org/abs/2106.15147}

\bibitem{yoon2020vime}
J. Yoon, Y. Zhang, J. Jordon, and M. van der Schaar.
\newblock \textit{VIME: Extending the Success of Self- and Semi-supervised Learning to Tabular Domain}.
\newblock NeurIPS, 2020.
\newblock \url{https://papers.nips.cc/paper/2020/hash/7d97667a3e056acab9aaf653807b4a03-Abstract.html}

\bibitem{uddin2021subtab}
M. P. Uddin et al.
\newblock \textit{SubTab: Subsetting Features of Tabular Data for Self-Supervised Representation Learning}.
\newblock NeurIPS, 2021.
\newblock \url{https://arxiv.org/abs/2110.04361}

\bibitem{mcpArchitecture}
Model Context Protocol.
\newblock \textit{Architecture Overview}.
\newblock Official MCP documentation.
\newblock \url{https://modelcontextprotocol.io/docs/learn/architecture}

\bibitem{mcpLatest}
Model Context Protocol.
\newblock \textit{Specification}.
\newblock Official MCP specification.
\newblock \url{https://modelcontextprotocol.io/specification/latest}

\bibitem{mcpPythonSdk}
Model Context Protocol.
\newblock \textit{MCP Python SDK}.
\newblock \url{https://modelcontextprotocol.github.io/python-sdk/}

\bibitem{wu2023autogen}
Q. Wu et al.
\newblock \textit{AutoGen: Enabling Next-Gen LLM Applications via Multi-Agent Conversation}.
\newblock arXiv:2308.08155, 2023.
\newblock \url{https://arxiv.org/abs/2308.08155}

\bibitem{langgraphDocs}
LangChain.
\newblock \textit{LangGraph Documentation}.
\newblock \url{https://docs.langchain.com/langgraph}

\bibitem{owaspLLM}
OWASP Foundation.
\newblock \textit{Top 10 for Large Language Model Applications}.
\newblock \url{https://owasp.org/www-project-top-10-for-large-language-model-applications/}

\bibitem{nistAI600}
National Institute of Standards and Technology.
\newblock \textit{Artificial Intelligence Risk Management Framework: Generative Artificial Intelligence Profile}.
\newblock NIST AI 600-1, 2024.
\newblock \url{https://doi.org/10.6028/NIST.AI.600-1}

\bibitem{fastapiDocs}
FastAPI.
\newblock \textit{FastAPI Documentation}.
\newblock \url{https://fastapi.tiangolo.com/}

\bibitem{pydanticJsonSchema}
Pydantic.
\newblock \textit{JSON Schema Documentation}.
\newblock \url{https://docs.pydantic.dev/latest/concepts/json_schema/}

\bibitem{pgvector}
pgvector.
\newblock \textit{Open-source vector similarity search for Postgres}.
\newblock \url{https://github.com/pgvector/pgvector}

\bibitem{dockerCompose}
Docker.
\newblock \textit{Docker Compose Documentation}.
\newblock \url{https://docs.docker.com/compose}

\bibitem{synthea}
The MITRE Corporation.
\newblock \textit{Synthea: Synthetic Patient Population Simulator}.
\newblock \url{https://synthetichealth.github.io/synthea/}

\bibitem{fhirR4}
HL7 International.
\newblock \textit{FHIR Release 4 Specification}.
\newblock \url{https://hl7.org/fhir/r4/}

\bibitem{bulkFHIR}
HL7 International.
\newblock \textit{FHIR Bulk Data Access (Flat FHIR)}.
\newblock \url{https://hl7.org/fhir/uv/bulkdata/}

\bibitem{omopCDM}
Observational Health Data Sciences and Informatics.
\newblock \textit{OMOP Common Data Model}.
\newblock \url{https://ohdsi.github.io/CommonDataModel/}

\bibitem{mimiciv}
PhysioNet.
\newblock \textit{MIMIC-IV}.
\newblock \url{https://physionet.org/content/mimiciv/}

\bibitem{eicu}
PhysioNet.
\newblock \textit{eICU Collaborative Research Database}.
\newblock \url{https://physionet.org/content/eicu-crd/2.0/}

\bibitem{n2c2}
National NLP Clinical Challenges.
\newblock \textit{n2c2 / i2b2 Clinical NLP Data Sets}.
\newblock \url{https://www.i2b2.org/NLP/DataSets/}

\bibitem{mimiccxr}
A. E. W. Johnson et al.
\newblock \textit{MIMIC-CXR, a de-identified publicly available database of chest radiographs with free-text reports}.
\newblock Scientific Data, 2019.
\newblock \url{https://www.nature.com/articles/s41597-019-0322-0}

\bibitem{chexpert}
Stanford AIMI.
\newblock \textit{CheXpert: Chest X-rays}.
\newblock \url{https://aimi.stanford.edu/datasets/chexpert-chest-x-rays}

\bibitem{jin2020medqa}
D. Jin et al.
\newblock \textit{What Disease does this Patient Have? A Large-scale Open Domain Question Answering Dataset from Medical Exams}.
\newblock arXiv:2009.13081, 2020.
\newblock \url{https://arxiv.org/abs/2009.13081}

\bibitem{pal2022medmcqa}
A. Pal, L. Umapathi, and M. Sankarasubbu.
\newblock \textit{MedMCQA: A Large-scale Multi-Subject Multi-Choice Dataset for Medical Domain Question Answering}.
\newblock arXiv:2203.14371, 2022.
\newblock \url{https://arxiv.org/abs/2203.14371}

\bibitem{jin2019pubmedqa}
Q. Jin et al.
\newblock \textit{PubMedQA: A Dataset for Biomedical Research Question Answering}.
\newblock EMNLP, 2019.
\newblock \url{https://arxiv.org/abs/1909.06146}

\bibitem{hipaaDeid}
U.S. Department of Health and Human Services.
\newblock \textit{Methods for De-identification of Protected Health Information}.
\newblock \url{https://www.hhs.gov/hipaa/for-professionals/privacy/special-topics/de-identification/}

\bibitem{imdrfSamd}
International Medical Device Regulators Forum.
\newblock \textit{Software as a Medical Device: Key Definitions}.
\newblock \url{https://www.imdrf.org/documents/software-medical-device-samd-key-definitions}

\bibitem{fdaGMLP}
U.S. Food and Drug Administration.
\newblock \textit{Good Machine Learning Practice for Medical Device Development: Guiding Principles}.
\newblock \url{https://www.fda.gov/medical-devices/software-medical-device-samd/good-machine-learning-practice-medical-device-development-guiding-principles}

\bibitem{fdaPCCP}
U.S. Food and Drug Administration.
\newblock \textit{Marketing Submission Recommendations for a Predetermined Change Control Plan for Artificial Intelligence-Enabled Device Software Functions}.
\newblock FDA guidance, 2025.

\bibitem{futureAI}
K. Lekadir et al.
\newblock \textit{FUTURE-AI: International Consensus Guideline for Trustworthy and Deployable Artificial Intelligence in Healthcare}.
\newblock BMJ, 2025.
\newblock \url{https://www.bmj.com/content/388/bmj-2024-081554}

\bibitem{tripodAI}
G. S. Collins et al.
\newblock \textit{TRIPOD+AI Statement: Updated Guidance for Reporting Clinical Prediction Models}.
\newblock BMJ, 2024.
\newblock \url{https://www.bmj.com/content/385/bmj.q902}

\bibitem{consortAI}
X. Liu et al.
\newblock \textit{Reporting Guidelines for Clinical Trial Reports for Interventions Involving Artificial Intelligence: The CONSORT-AI Extension}.
\newblock Nature Medicine, 2020.
\newblock \url{https://www.nature.com/articles/s41591-020-1034-x}

\bibitem{claimAI}
J. Mongan et al.
\newblock \textit{Checklist for Artificial Intelligence in Medical Imaging (CLAIM)}.
\newblock Radiology: Artificial Intelligence, 2020.
\newblock \url{https://pubs.rsna.org/doi/10.1148/ryai.2020200029}

\bibitem{qdrant}
Qdrant.
\newblock \textit{Qdrant Vector Search Engine Documentation}.
\newblock \url{https://qdrant.tech/documentation/overview/}

\bibitem{milvus}
Milvus.
\newblock \textit{High-Performance Vector Database Built for Scale}.
\newblock \url{https://milvus.io/}

\bibitem{feast}
Feast.
\newblock \textit{The Open Source Feature Store for Machine Learning}.
\newblock \url{https://docs.feast.dev/}

\bibitem{mlflowRegistry}
MLflow.
\newblock \textit{MLflow Model Registry}.
\newblock \url{https://mlflow.org/docs/latest/ml/model-registry/}

\bibitem{dvc}
Data Version Control.
\newblock \textit{Versioning Data and Models}.
\newblock \url{https://dvc.org/doc/use-cases/versioning-data-and-models}

\bibitem{opentelemetry}
OpenTelemetry.
\newblock \textit{OpenTelemetry Documentation}.
\newblock \url{https://opentelemetry.io/docs/}

\bibitem{prometheus}
Prometheus.
\newblock \textit{Overview}.
\newblock \url{https://prometheus.io/docs/introduction/overview/}

\bibitem{evidently}
Evidently AI.
\newblock \textit{Open-Source ML Monitoring and LLM Observability}.
\newblock \url{https://www.evidentlyai.com/evidently-oss}

\bibitem{githubActions}
GitHub.
\newblock \textit{GitHub Actions Documentation}.
\newblock \url{https://docs.github.com/en/actions}

\bibitem{workloadIdentityFederation}
Google Cloud.
\newblock \textit{Workload Identity Federation}.
\newblock \url{https://cloud.google.com/iam/docs/workload-identity-federation}

\bibitem{githubOIDCGCP}
GitHub.
\newblock \textit{Configuring OpenID Connect in Google Cloud Platform}.
\newblock \url{https://docs.github.com/en/actions/security-for-github-actions/security-hardening-your-deployments/configuring-openid-connect-in-google-cloud-platform}

\bibitem{argoCD}
Argo CD.
\newblock \textit{Declarative GitOps CD for Kubernetes}.
\newblock \url{https://argo-cd.readthedocs.io/}

\bibitem{kubeflowPipelines}
Kubeflow.
\newblock \textit{Kubeflow Pipelines}.
\newblock \url{https://www.kubeflow.org/docs/components/pipelines/concepts/pipeline/}

\bibitem{cloudDeployGKE}
Google Cloud.
\newblock \textit{Deploy an App to GKE using Cloud Deploy}.
\newblock \url{https://cloud.google.com/deploy/docs/deploy-app-gke}

\bibitem{kserve}
KServe.
\newblock \textit{Standardized Distributed Inference Platform on Kubernetes}.
\newblock \url{https://kserve.github.io/kserve/}

\bibitem{vllm}
vLLM.
\newblock \textit{High-Throughput and Memory-Efficient LLM Serving}.
\newblock \url{https://www.vllm.ai/}

\bibitem{rayServe}
Ray.
\newblock \textit{Ray Serve: Scalable and Programmable Serving}.
\newblock \url{https://docs.ray.io/en/latest/serve/}

\bibitem{gcpHealthcare}
Google Cloud.
\newblock \textit{Cloud Healthcare API}.
\newblock \url{https://cloud.google.com/healthcare-api}

\bibitem{bigquery}
Google Cloud.
\newblock \textit{BigQuery Overview}.
\newblock \url{https://docs.cloud.google.com/bigquery/docs/introduction}

\bibitem{gke}
Google Cloud.
\newblock \textit{Google Kubernetes Engine Documentation}.
\newblock \url{https://docs.cloud.google.com/kubernetes-engine/docs/about}

\bibitem{cloudBuild}
Google Cloud.
\newblock \textit{Cloud Build Documentation}.
\newblock \url{https://cloud.google.com/build/docs}

\bibitem{artifactRegistry}
Google Cloud.
\newblock \textit{Artifact Registry Supported Formats}.
\newblock \url{https://docs.cloud.google.com/artifact-registry/docs/supported-formats}

\bibitem{vertexPipelines}
Google Cloud.
\newblock \textit{Introduction to Vertex AI Pipelines}.
\newblock \url{https://cloud.google.com/vertex-ai/docs/pipelines/introduction}

\bibitem{vertexVectorSearch}
Google Cloud.
\newblock \textit{Vertex AI Vector Search}.
\newblock \url{https://docs.cloud.google.com/vertex-ai/docs/vector-search/overview}

\bibitem{secretManager}
Google Cloud.
\newblock \textit{Secret Manager Overview}.
\newblock \url{https://docs.cloud.google.com/secret-manager/docs/overview}

\bibitem{vpcServiceControls}
Google Cloud.
\newblock \textit{Overview of VPC Service Controls}.
\newblock \url{https://docs.cloud.google.com/vpc-service-controls/docs/overview}

\bibitem{umls}
U.S. National Library of Medicine.
\newblock \textit{Unified Medical Language System}.
\newblock \url{https://www.nlm.nih.gov/research/umls/index.html}

\bibitem{snomed}
SNOMED International.
\newblock \textit{SNOMED CT}.
\newblock \url{https://www.snomed.org/snomed-ct}

\bibitem{loinc}
Regenstrief Institute.
\newblock \textit{LOINC}.
\newblock \url{https://loinc.org/}

\bibitem{rxnorm}
U.S. National Library of Medicine.
\newblock \textit{RxNorm}.
\newblock \url{https://www.nlm.nih.gov/research/umls/rxnorm/index.html}

\bibitem{japanAgingSociety}
Cabinet Office, Government of Japan.
\newblock \textit{Annual Report on the Ageing Society 2025}.
\newblock \url{https://www8.cao.go.jp/kourei/english/annualreport/index-wh.html}

\bibitem{mhlwMedicalDX}
Ministry of Health, Labour and Welfare, Japan.
\newblock \textit{Medical DX}.
\newblock \url{https://www.mhlw.go.jp/stf/iryoudx.html}

\bibitem{mhlwMedicalDXRoadmap}
Ministry of Health, Labour and Welfare, Japan.
\newblock \textit{Roadmap for the Promotion of Healthcare DX}.
\newblock \url{https://www.mhlw.go.jp/english/policy/health-medical/healthcare-dx/dl/Roadmap-for-the-Promotion-of-Healthcare-DX%28Digital-Transformation%29.pdf}

\bibitem{japanAPPI}
Personal Information Protection Commission, Japan.
\newblock \textit{Act on the Protection of Personal Information}.
\newblock \url{https://www.ppc.go.jp/files/pdf/APPI_english.pdf}

\bibitem{mhlwMedicalInfoSecurity}
Ministry of Health, Labour and Welfare, Japan.
\newblock \textit{Guidelines on Safety Management of Healthcare Information Systems Version 6.0}.
\newblock \url{https://www.mhlw.go.jp/stf/shingi/0000516275_00006.html}

\bibitem{pmdaSaMD}
Pharmaceuticals and Medical Devices Agency.
\newblock \textit{Software as a Medical Device}.
\newblock \url{https://www.pmda.go.jp/english/review-services/reviews/0009.html}

\bibitem{jpCore}
FHIR Japanese Implementation Research Working Group.
\newblock \textit{HL7 FHIR JP Core Implementation Guide}.
\newblock \url{https://www.jpfhir.jp/fhir/core/latest/guide-general.html}

\bibitem{japanBusinessCulture}
Global Business Culture.
\newblock \textit{Japan Business Culture Guide: Communication, Leadership, and Decision-Making}.
\newblock \url{https://www.globalbusinessculture.com/countries/japan/japan-business-culture/}

\bibitem{gcpDocumentAI}
Google Cloud.
\newblock \textit{Enterprise Document OCR}.
\newblock \url{https://docs.cloud.google.com/document-ai/docs/enterprise-document-ocr}

\bibitem{sam2023}
Alexander Kirillov, Eric Mintun, Nikhila Ravi, Hanzi Mao, Chloe Rolland, Laura Gustafson, Tete Xiao, Spencer Whitehead, Alexander C. Berg, Wan-Yen Lo, Piotr Dollar, and Ross Girshick.
\newblock \textit{Segment Anything}.
\newblock arXiv:2304.02643, 2023.
\newblock \url{https://arxiv.org/abs/2304.02643}

\bibitem{medsam2024}
Jun Ma, Yuting He, Feifei Li, Lin Han, Chenyu You, and Bo Wang.
\newblock \textit{Segment Anything in Medical Images}.
\newblock Nature Communications, 15:654, 2024.
\newblock \url{https://www.nature.com/articles/s41467-024-44824-z}

\bibitem{sam2}
Nikhila Ravi et al.
\newblock \textit{SAM 2: Segment Anything in Images and Videos}.
\newblock arXiv:2408.00714, 2024.
\newblock \url{https://arxiv.org/abs/2408.00714}

\bibitem{medsam2}
Junde Wu et al.
\newblock \textit{Medical SAM 2: Segment Medical Images as Video via Segment Anything Model 2}.
\newblock arXiv:2408.00874, 2024.
\newblock \url{https://arxiv.org/abs/2408.00874}

\bibitem{nnunet}
Fabian Isensee, Paul F. Jaeger, Simon A. A. Kohl, Jens Petersen, and Klaus H. Maier-Hein.
\newblock \textit{nnU-Net: A Self-Configuring Method for Deep Learning-Based Biomedical Image Segmentation}.
\newblock Nature Methods, 18:203--211, 2021.
\newblock \url{https://www.nature.com/articles/s41592-020-01008-z}

\bibitem{totalSegmentator}
Jakob Wasserthal et al.
\newblock \textit{TotalSegmentator: Robust Segmentation of 104 Anatomical Structures in CT Images}.
\newblock arXiv:2208.05868, 2022.
\newblock \url{https://arxiv.org/abs/2208.05868}

\bibitem{monaiLabel}
MONAI Consortium.
\newblock \textit{MONAI Label Documentation}.
\newblock \url{https://docs.monai.io/projects/label}

\bibitem{nndetection}
Michael Baumgartner, Paul F. Jaeger, Fabian Isensee, and Klaus H. Maier-Hein.
\newblock \textit{nnDetection: A Self-Configuring Method for Medical Object Detection}.
\newblock arXiv:2106.00817, 2021.
\newblock \url{https://arxiv.org/abs/2106.00817}

\end{thebibliography}
